Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-24 paper/paper.tex
Updates from Overleaf

The rest of the paper proceeds as follows. Section 2 presents some background information. Section 3 describes the data used in the analysis. Section 4 details the empirical approach. Section 5 presents results. Section 6 discusses implications and robustness of the results. Section 7 concludes.

\section{Historical background}

Early modern Europe consisted of many large and small states.

One story about a city's territory switch

Two pithy figures, and a no-nonsense table

NO MORE THAN TWO PAGES TOTAL

@@

I use data from the \textit{Princes and Townspeople} database which is largely based on the \textit{Deutsches Städtebuch} \citep{keyser1939} and \cite{kobler2007}'s \textit{Historisches Lexikon der Deutschen Länder}. The specific datasets I use are those on city locations \citep{pt1}, territorial histories \citep{pt2}, construction activity \citep{pt5} and conflict incidents \citep{pt6}.\footnote{I thank Davide Cantoni and Matthias Weigand for giving me access to unpublished yearly versions of the construction and territorial histories data.} I aggregate data from these sources to obtain a city-by-year panel of switching events, construction activity, and conflict.

Switching: describe format; total number of recorded switches; territory id.

@@

\section{Regression equations}

@@

\section{Results}

@@

\section{Discussion}

@@

\section{Conclusion}

@@

@@

>>>>

The rest of the paper proceeds as follows. Section \ref{sec:data} describes the data used in the analysis. Section \ref{sec:empirics} details the empirical approach. Section \ref{sec:results} presents results. Section \ref{sec:discussion} discusses implications and robustness of the results. Section \ref{sec:conclusion} concludes.

@@

I use data from the \textit{Princes and Townspeople} database which is largely based on the \textit{Deutsches Städtebuch} \citep{keyser1939} and \cite{kobler2007}'s \textit{Historisches Lexikon der Deutschen Länder}. The specific datasets I use are those on city locations \citep{pt1}, territorial histories \citep{pt2}, construction activity \citep{pt5} and conflict incidents \citep{pt6}.\footnote{I thank Davide Cantoni and Matthias Weigand for giving me access to unpublished yearly versions of the construction and territorial histories data.}

I aggregate data from these sources to obtain a panel of

- unit of observation: city-year / city-period
- precision of time points
- aggregation of years
- unbalanced panel
- definition of territory holding
- definition of switch in period
- justification for using construction
- different groupings of construction
- scope of the data / regions included
- time period recorded
- missing values / full sequence of event years
- dropNA construction -> sample size

@@

\section{Regression equations} \label{sec:empirics}

@@

\section{Results} \label{sec:results}

@@

\section{Discussion} \label{sec:discussion}

@@

\section{Conclusion} \label{sec:conclusion}

@@

\begin{figure}
    \centering
    \includegraphics{}
    \caption{Caption}
    \label{fig:enter-label}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[scale = 0.15]{paper/output/descriptive/map_conflict_NA_50y.png}
    \caption{Share of observations remaining from each \textit{Städtebuch} region when controlling for conflict incidents in Equation \eqref{eq:baseline}. Geo-referenced borders of the regions were not available; this makeshift visualisation shows convex hulls of the city locations in each region (which results in some overlap.)}
    \label{fig:conflict_map}
\end{figure}
